---
title: "Analysis: Neuser et al (2020) replication study "
output: html_notebook
---=
---

Clear workspace

```{r}
rm(list= ls(all.names = TRUE))
gc()
```

Load in libraries

```{r}
# load in libraries 
library(ggplot2)
library(stats)
library(RColorBrewer)
library(plyr)
library(dplyr)
library(tidyverse)
library(BayesFactor)
library(gridExtra)
library(psychometric)
library(lmerTest)
library(viridis)
library(sjPlot)
library(htmltools)
library(webshot)
library(haven)
library(Rmisc)
library(tidyr)
library(ggridges)
library(esc)
library(lsr)
library(robustbase)
```

## Settings

Choose which dataset to run analysis on:

-   Neuser et al. original data from [OSF \| Vagus nerve stimulation boosts the drive to work for rewards](https://osf.io/58r3c/?view_only=5d1ccee7d67b464bb6f40ebe7ebc844b)

-   Leiden replication data (collected 2021-2022)

```{r}
dataset_ana = 'Leiden_repl' #'Leiden_repl' / 'Neuser_orig'
```

Load in pre-processed data

```{r}
home_path = 'C:/Users/lloydb/surfdrive/ExperimentData/projects/Neuser_task/Tasks-master/Effort_Allocation_Task/Data/TUE001/Processed'

if (dataset_ana == 'Neuser_orig') {
  df <- haven::read_sav(paste(home_path, 'Neuser_orig_dat', 'Neuseretal2020_taVNS_EAT_source_file_OSF.sav', sep='/'))
  df <- as.data.frame(df_sav)
  print(paste('Running analysis on Neuser original data, including ', length(unique(df$ID)), ' participants!', sep=""))
  fig_path = 'C:/Users/lloydb/surfdrive/ExperimentData/projects/Neuser_task/Tasks-master/Effort_Allocation_Task/stats/Neuser_orig_figures/'
  
} else if (dataset_ana == 'Leiden_repl') {
  df <- read.csv(paste(home_path, '20230112', 'EAT_TUE001_Exp_Merg+Seg_AggrTrial_20230112.csv', sep='/'))
 
  fig_path = 'C:/Users/lloydb/surfdrive/ExperimentData/projects/Neuser_task/Tasks-master/Effort_Allocation_Task/stats/Leiden_repl_figures/'
  # remove sub 103 (only 1 session) and 129 (did not respond to too many trials)
  df <- subset(df, Subj_ID != '103')
  df <- subset(df, Subj_ID != '129')
  print(paste('Running analysis on Leiden replication data, including ', length(unique(df$Subj_ID)), ' participants!', sep=""))
}

```

Only for Leiden data!

-   load in the session order file: [1 = tvns \> sham, 0 = sham \> tvns] and add it to dataframe

-   rename some variables (all in-line with Neuser original data)

-   re-code some variables (all in-line with Neuser original data)

-   make 2nd level order dataset and save both files as .sav file (for HLM)

```{r}
if (dataset_ana == 'Leiden_repl') {
  order_var <- read.csv(paste(home_path, '20230112', 'sess_Order.csv', sep='/'), sep=';')
  df <- left_join(df, order_var, by='Subj_ID')
  df <- df %>% 
  rename(Food = Rew_type,
    RewM = Rew_mag,
    cDiff = Diff,
    Order = sess_order,
    RelFreq = RelEffort,
    ID = Subj_ID, 
    Rating_exh = R_Exh,
    Rating_want = R_Want, 
    SessNr = Sess_ID)
  # re-code
  df <- df %>%
  mutate(RewM = case_when(RewM == 10 ~ 1,
                          RewM == 1 ~ 0))
  df <- df %>%
  mutate(cDiff = case_when(cDiff == 85 ~ 1,
                           cDiff == 75 ~ 0))
  df <- df %>%
  mutate(I_DRM = case_when(cDiff == 1 & RewM == 1 ~ 0.5,
                           cDiff == 1 & RewM == 0 ~ -0.5,
                           cDiff == 0 & RewM == 1 ~ -0.5,
                           cDiff == 0 & RewM == 0 ~ 0.5))
  df <- df %>%
  mutate(I_SDiff = case_when(cDiff == 1 & StimCond == 1 ~ 0.5,
                           cDiff == 1 & StimCond == 0 ~ -0.5,
                           cDiff == 0 & StimCond == 1 ~ -0.5,
                           cDiff == 0 & StimCond == 0 ~ 0.5))
  df <- df %>%
  mutate(I_SRewM = case_when(StimCond == 1 & RewM == 1 ~ 0.5,
                             StimCond == 1 & RewM == 0 ~ -0.5,
                             StimCond == 0 & RewM == 1 ~ -0.5,
                             StimCond == 0 & RewM == 0 ~ 0.5))
  df <- df %>%
  mutate(I_SFood = case_when(StimCond == 1 & Food == 1 ~ 0.5,
                             StimCond == 1 & Food == 0 ~ -0.5,
                             StimCond == 0 & Food == 1 ~ -0.5,
                             StimCond == 0 & Food == 0 ~ 0.5))
  df <- df %>%
  mutate(I_SDRM = case_when(StimCond == 1 & I_DRM == 0.5 ~ 0.5,
                             StimCond == 1 & I_DRM == -0.5 ~ -0.5,
                             StimCond == 0 & I_DRM == 0.5 ~ -0.5,
                             StimCond == 0 & I_DRM == -0.5 ~ 0.5))
  
  df <- df %>%
  mutate(Split_Half = case_when(Trial_ID <= 24 ~ 0,
                             Trial_ID > 24 ~ 1))
  
  df <- df %>%
  mutate(I_SSplit_Half = case_when(StimCond == 0 & Split_Half == 0 ~ 0.5,
                             StimCond == 1 & Split_Half == 0 ~ -0.5,
                             StimCond == 1 & Split_Half == 1 ~ 0.5,
                             StimCond == 0 & Split_Half == 1 ~ -0.5))
  
  # save 2nd level variables for HLM analysis
  #second_level_vars <- aggregate(cbind(Order)
   #                             ~ ID, data = df, FUN = function(x) c(mn = mean(x)))
}
  
  # replace the missing trial slope with the average of the session. 

#write_sav(second_level_vars, paste(home_path, '/20230112/2nd_level_variable.sav', sep=''))
#write_sav(df, paste(home_path, '/20230112/1st_level_variables_trialLevel_Neuser.sav', sep=''))
print('saved Leiden data as .sav files !')
```

```{r}
if (dataset_ana == 'Neuser_orig'){
  df <- df %>%
  mutate(Order = case_when(SessNr == 1 & StimCond == 1 ~ 1,
                           SessNr == 2 & StimCond == 1 ~ 0,
                           SessNr == 1 & StimCond == 0 ~ 0,
                           SessNr == 2 & StimCond == 0 ~ 1))
}
```

2.  **Carry out analyses not done in HLM**

Some variable settings

```{r}
df$ID <- as.numeric(df$ID)
df$cDiff <- as.numeric(df$cDiff)
df$RewM <- as.numeric(df$RewM)
df$Food <- as.numeric(df$Food)
df$StimCond <- as.numeric(df$StimCond)
df$S_InvSlope <- as.numeric(df$S_InvSlope)
df$RelFreq <- as.numeric(df$RelFreq)
```

**Correlation: invigoration x effort maintenance**

```{r}
cor_df <- df %>% drop_na(S_InvSlope) # NA in invig slope for 40 rows for Leiden dat

r_val <- cor(cor_df$RelFreq, cor_df$S_InvSlope, method = "pearson")
conf_interval_cor <- CIr(r=r_val, n = length(cor_df$S_InvSlope), level = .95)

print(paste('correlation between inv and effort maintenance is r = ', round(r_val,3), ' CI = ', '[', round(conf_interval_cor[1], 2), ', ', round(conf_interval_cor[2], 2), ']', sep=''))


```

tion_data %\>% filter(SessNr == 2) %\>% pull(S_InvSlope)

)

\# create scatter plot with regression line

ggplot(clean_invigoration_data, aes(x = S_InvSlope, y = S_InvSlope, color = SessNr)) +

geom_point(data = sess1_data, aes(x = S_InvSlope, y = S_InvSlope), size = 3) +

geom_point(data = sess2_data, aes(x = S_InvSlope, y = S_InvSlope), size = 3) +

stat_smooth(method = "lm", formula = y \~ x, se = FALSE) +

ggtitle(paste("Correlation:", round(correlation, 2)))

```{r}
# First, create a subset of the data with only the invigoration scores and participant IDs
invigoration_data <- df[, c("ID", "SessNr", "S_InvSlope")]
invigoration_data$SessNr <- as.factor(invigoration_data$SessNr)
invigoration_data$S_InvSlope <- as.numeric(invigoration_data$S_InvSlope)


agg_inv = describeBy(S_InvSlope ~ SessNr + ID, data = invigoration_data, mat = TRUE)



# calculate correlation coefficient
correlation <- cor(
  agg_inv %>% filter(group1 == 1) %>% pull(mean),
  agg_inv %>% filter(group1 == 2) %>% pull(mean)
)



# filter data for SessNr == 1 and SessNr == 2
sess1_data <- agg_inv %>% filter(group1 == 1)
sess2_data <- agg_inv %>% filter(group1 == 2)

# calculate correlation between S_InvSlope for SessNr == 1 and SessNr == 2
correlation <- cor(sess1_data$mean, sess2_data$mean)

ggplot(data = data.frame(x = sess1_data$mean, y = sess2_data$mean), aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("SessNr 1") +
  ylab("SessNr 2") + mytheme + 
  ggtitle(paste("Pearson correlation:", round(cor(sess1_data$mean, sess2_data$mean), 2)))


```

```{r}
# First, create a subset of the data with only the invigoration scores and participant IDs
RelFreq_data <- df[, c("ID", "SessNr", "RelFreq")]
RelFreq_data$SessNr <- as.factor(RelFreq_data$SessNr)
RelFreq_data$RelFreq <- as.numeric(RelFreq_data$RelFreq)


agg_inv = describeBy(RelFreq ~ SessNr + ID, data = RelFreq_data, mat = TRUE)



# calculate correlation coefficient
correlation <- cor(
  agg_inv %>% filter(group1 == 1) %>% pull(mean),
  agg_inv %>% filter(group1 == 2) %>% pull(mean)
)



# filter data for SessNr == 1 and SessNr == 2
sess1_data <- agg_inv %>% filter(group1 == 1)
sess2_data <- agg_inv %>% filter(group1 == 2)

# calculate correlation between S_InvSlope for SessNr == 1 and SessNr == 2
correlation <- cor(sess1_data$mean, sess2_data$mean)

ggplot(data = data.frame(x = sess1_data$mean, y = sess2_data$mean), aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("SessNr 1") +
  ylab("SessNr 2") + mytheme + 
  ggtitle(paste("Pearson correlation:", round(cor(sess1_data$mean, sess2_data$mean), 2)))

```

```{r}

```

## Mixed models: lmerTest

(code received from Nils on 06/10/2022)

```{r}
ave_subjs_ratings_want <- summarySE(df, measurevar="Rating_want", groupvars=c("ID"))

sums_want <- sapply(ave_subjs_ratings_want, mean, na.rm=TRUE)
paste('average wanting rating: ', sums_want[3], sep = '')

```

```{r}
ave_subjs_ratings_ex <- summarySE(df, measurevar="Rating_exh", groupvars=c("ID"))

sums_ex <- sapply(ave_subjs_ratings_ex, mean, na.rm=TRUE)
paste('average exertion rating: ', sums_ex[3], sep = '')
```

```{r}

## preparing dataset for plotting later (checking the ratings distributions!)
if (dataset_ana == 'Leiden_repl') {
  df_subjs_vars <- list()
  df_subjs_vars$leiden_wanting <- scale(df$Rating_want)
  df_subjs_vars$leiden_exertion <- scale(df$Rating_exh)
  #$SessNr <- df$SessNr 
  df_subjs_vars <- as.data.frame(df_subjs_vars)
  
  df_subjs_vars_leiden = tidyr::gather(df_subjs_vars, value=Val, key=Names, leiden_wanting:leiden_exertion, factor_key=TRUE)
} else if (dataset_ana == 'Neuser_orig') {
  df_subjs_vars <- list()
  df_subjs_vars$neuser_wanting <- scale(df_neuser$Rating_want)
  df_subjs_vars$neuser_exertion <- scale(df_neuser$Rating_exh)
  
  df_subjs_vars <- as.data.frame(df_subjs_vars)
  
  df_subjs_vars_neuser = tidyr::gather(df_subjs_vars, value=Val, key=Names, neuser_wanting:neuser_exertion, factor_key=TRUE) 
}
```

PREP for mixed models

```{r}

# center variables
df$cRate_W <- df$Rating_want - mean(df$Rating_want)
df$cRate_E <- df$Rating_exh  - mean(df$Rating_exh)

```

Note that these lmer models don't reach convergence. Checked with original data from Neuser et al., and results are inline with the way these ran

```{r}
if (dataset_ana == 'Leiden_repl') {
  
  # remove 50 responses for Leiden dataset (see paper for explanation)
  df_clean = subset(df, Rating_want != 50.000000)
  df_clean = subset(df_clean, Rating_exh != 50.000000)
  
  df_clean$USE_cRate_W <- df_clean$Rating_want - mean(df_clean$Rating_want)
  df_clean$USE_cRate_E <- df_clean$Rating_exh  - mean(df_clean$Rating_exh)
  fm1 <-lmerTest::lmer(S_InvSlope ~ USE_cRate_W + USE_cRate_E + (USE_cRate_E + USE_cRate_E | ID), df_clean)
  summary(fm1)
  fm1_sum <- summary(fm1)
  
  options(scipen=999)
} else if (dataset_ana == 'Neuser_orig') {
  # center variables
  df$cRate_W <- df$Rating_want - mean(df$Rating_want)
  df$cRate_E <- df$Rating_exh  - mean(df$Rating_exh)
  fm1 <-lmerTest::lmer(S_InvSlope ~ cRate_W + cRate_E + (USE_cRate_E + cRate_E | ID), df)
  summary(fm1)
  fm1_sum <- summary(fm1)
  
  options(scipen=999)
}

```

```{r}

```

Predicting effort maintenance \~ wanting and exertion (same convergence issue as above)

long_indiv_betas_refreq = tidyr::gather(indiv_betas_refreq, value=beta, key=Condition, cRate_W:cRate_E, factor_key=TRUE)

```{r}
if (dataset_ana == 'Leiden_repl') {

  fm2 <- lmerTest::lmer(RelFreq ~ USE_cRate_W + USE_cRate_E + (USE_cRate_W + USE_cRate_E | ID), df_clean)
  summary(fm2)
  fm2_sum <- summary(fm2)
} else if (dataset_ana == 'Neuser_orig') {
  
  fm2 <- lmerTest::lmer(RelFreq ~ cRate_W + cRate_E + (cRate_W + cRate_E | ID), df)
  summary(fm2)
  fm2_sum <- summary(fm2)
}

```

```{}
```

```{}
```

(Response to Nils Oct 2022): Check EFFECT SIZE of Reward magnitude effect

-   collapse across RewM and run cohensd on paired data

```{r}
if (dataset_ana == 'Neuser_orig') {
left_side <- subset(df, StimSide == 0)
right_side <- subset(df, StimSide == 1)
ave_RewM_inv <- summarySE(right_side, measurevar="S_InvSlope", na.rm = TRUE, groupvars=c("ID", "RewM"))
ave_RewM_relfreq<- summarySE(right_side, measurevar="RelFreq", na.rm = TRUE, groupvars=c("ID", "RewM"))
inv <- cohensD(S_InvSlope ~ RewM,
       data   = ave_RewM_inv,
       method = "paired")
relfreq <- cohensD(RelFreq ~ RewM,
       data   = ave_RewM_relfreq,
       method = "paired")
}
```

Run the robust regression for plot 5a (on group level)

```{r}
if (dataset_ana == 'Leiden_repl') {
ave_data_fig5a <- aggregate(cbind(S_InvSlope, Rating_want)
                             ~ ID + StimCond + Food, data = df, FUN = function(x) c(mn = mean(x) ) )
}
if (dataset_ana == 'Neuser_orig') {
ave_data_fig5a <- aggregate(cbind(S_InvSlope, Rating_want)
                             ~ ID + StimCond + Food + StimSide, data = df, FUN = function(x) c(mn = mean(x) ) )
}

#rmodel <- robustbase::lmrob(S_InvSlope ~ Rating_want + attraction, data = ave_data_fig5a)

```

## Plot data

```{r}
mytheme <- theme(panel.grid.major = element_blank(), 
                 panel.grid.minor = element_blank(),
                 panel.background = element_blank(), 
                 axis.line = element_line(size=0.8, colour = "black"),
                 text = element_text(size=16,colour = "black"),
                 strip.background = element_blank())
```

plot settings:

```{r}
# recode the variable names: for plotting only
df <- df %>%
  mutate(RewM = case_when(RewM == 1 ~ 'High',
                          RewM == 0 ~ 'Low'))

df <- df %>%
  mutate(StimCond = case_when(StimCond == 0 ~ 'Sham',
                             StimCond == 1 ~ 'taVNS'))
df <- df %>%
  mutate(Food = case_when(Food == 0 ~ 'Money',
                          Food == 1 ~ 'Food'))
df <- df %>%
  mutate(cDiff = case_when(cDiff == 0 ~ 'Easy',
                           cDiff == 1 ~ 'Hard'))

df <- df %>%
  mutate(Order = case_when(Order == 1 ~ 'tVNS>sham',
                           Order == 0 ~ 'sham>tVNS'))

df$StimCond <- as.factor(df$StimCond)
df$Order <- as.factor(df$Order)
df$Food <- as.factor(df$Food)
df$SessNr <- as.factor(df$SessNr)

if (dataset_ana == 'Neuser_orig'){
  df <- df %>%
  mutate(StimSide = case_when(StimSide == 1 ~ 'Right ear',
                           StimSide == 0 ~ 'Left ear'))
  df$StimSide <- as.factor(df$StimSide)
}
```

==note: according to Neuser et al. all plots show averages across conditions and across session (so each participant has two points inside each bar)

**Settings for Figure 2 a-d**

```{r}
ave_data_fig2a <- summarySE(df, measurevar="S_InvSlope", groupvars=c("cDiff","RewM", "ID", "StimCond"))
ave_data_fig2b <- summarySE(df, measurevar="RelFreq", groupvars=c("cDiff","RewM", "ID", "StimCond"))
ave_data_fig2c <- summarySE(df, measurevar="S_InvSlope", groupvars=c("Food","RewM", "ID", "StimCond"))
ave_data_fig2d <- summarySE(df, measurevar="RelFreq", groupvars=c("Food","RewM", "ID", "StimCond"))

```

**Make Figure 2 a-d**

```{r}
require(gridExtra)
plot_A <- qplot(1)
plot_B <- qplot(1)
plot_C <- qplot(1)
plot_D <- qplot(1)


data=ave_data_fig2a[ave_data_fig2a$ID %in% c('103', '106'),]
# Fig 2. a)

plot_A <- ave_data_fig2a %>%
  mutate(RewM = fct_relevel(RewM,"Low", "High")) %>%
  ggplot(aes(x = cDiff, y = S_InvSlope, fill = RewM)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5, position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9), alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom = "errorbar", alpha=1, position=position_dodge(width=0.9)) +
  scale_fill_manual(values = c("#fe9929", "#2c7fb8")) +
  mytheme +
  guides(fill=guide_legend(title='Reward\nmagnitude')) +
  labs(title = "", x = "Difficulty", y = "Invigoration slope[%/s]") +
  scale_y_continuous(expand = c(0, 0))

# Fig 2. b)

plot_B <- ave_data_fig2b %>%
  mutate(RewM = fct_relevel(RewM,"Low", "High")) %>%
  ggplot(aes(x = cDiff, y = RelFreq, fill = RewM)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5,position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9), alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom = "errorbar", alpha=1, position=position_dodge(width=0.9)) +
  guides(fill=guide_legend(title='Reward\nmagnitude')) +
  scale_fill_manual(values = c("#fe9929", "#2c7fb8")) +
  mytheme   +     
  labs(title = "", x = "Difficulty", y = "Relative frequency[%]")  +
  scale_y_continuous(expand = c(0, 0))

# Fig 2. c)
plot_C <- ave_data_fig2c %>%
  mutate(Food = fct_relevel(Food,"Money", "Food")) %>%
  mutate(RewM = fct_relevel(RewM,"Low", "High")) %>%
  ggplot(aes(x = Food, y = S_InvSlope, fill = RewM)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5,position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9), alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom = "errorbar", alpha=1, position=position_dodge(width=0.9)) +
  scale_fill_manual(values = c("#fe9929", "#2c7fb8")) +
  mytheme   +
  guides(fill=guide_legend(title='Reward\nmagnitude')) +
  labs(title = "", x = "Reward type", y = "Invigoration Slope [%/s]")+
  scale_y_continuous(expand = c(0, 0))

# Fig 2. d)
plot_D <- ave_data_fig2d %>%
  mutate(Food = fct_relevel(Food,"Money", "Food")) %>%
  mutate(RewM = fct_relevel(RewM,"Low", "High")) %>%
  ggplot(aes(x = Food, y = RelFreq, fill = RewM)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5,position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9), alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom = "errorbar", alpha=1, position=position_dodge(width=0.9)) +
  guides(fill=guide_legend(title='Reward\nmagnitude')) +
  scale_fill_manual(values = c("#fe9929", "#2c7fb8")) +
  mytheme                 +                                 
  labs(title = "", x = "Reward type", y =  "Relative frequency[%]")+
  scale_y_continuous(expand = c(0, 0))

# Combine plots in one figure
plt_fig2 <- grid.arrange(plot_A, plot_B, plot_C, plot_D, nrow=2, ncol=2)
  labs(title = "Main effects of task conditions")
plt_fig2

#ggsave(path = fig_path, filename = "Fig_2abcd.pdf", plot=plt_fig2,  width = 8, height =8)

```

**Settings for Figure 2e**

```{r}
var_name <- c('Exertion invig', 'Exertion maintenance', 'Wanting invig', 'Wanting maintenance')
coeffs <- c(fm1_sum$coefficients[3], fm2_sum$coefficients[3], fm1_sum$coefficients[2], fm2_sum$coefficients[2])
min_err <- c(fm1_sum$coefficients[6], fm2_sum$coefficients[6], fm1_sum$coefficients[5], fm2_sum$coefficients[5])
# create dummy data
data_plot2e <- data.frame(
  name=var_name,
  value=coeffs,
  sem=min_err
)

```

```{r}
fig2e <- ggplot(data_plot2e) +
  geom_bar( aes(x=name, y=value), stat="identity", fill="skyblue", alpha=0.5) +
  geom_linerange( aes(x=name, ymin=value-sem, ymax=value+sem), colour="black", alpha=0.9, size=0.8) + mytheme

ggsave(path = fig_path, filename = "Fig_2e.pdf", plot=fig2e,  width = 6, height =4)
```

**Settings for Figure 3 a-d**

```{r}
# make average per subj, per condition of: Inv_slope and Rel_freq
if (dataset_ana == 'Neuser_orig'){
  ave_data_fig3a <- summarySE(df, measurevar="S_InvSlope", groupvars=c("Food","StimCond", "ID", "StimSide"))
  ave_data_fig3b <- summarySE(df, measurevar="RelFreq", groupvars=c("Food","StimCond", "ID", "StimSide"))
  
} else if ( dataset_ana == 'Leiden_repl') {
  ave_data_fig3a <- summarySE(df, measurevar="S_InvSlope", groupvars=c("Food","StimCond", "ID"))
  ave_data_fig3b <- summarySE(df, measurevar="RelFreq", groupvars=c("Food","StimCond", "ID"))
}

```

**Make Figure 3 a-b**

```{r}

## Plotting data: Figure 3.
require(gridExtra)
Fig3a <- qplot(1)
Fig3b <-qplot(1)

Fig3a <- ave_data_fig3a %>%
  mutate(Food = fct_relevel(Food,"Money", "Food")) %>%
  mutate(StimCond = fct_relevel(StimCond,"Sham", "taVNS")) %>%
  ggplot(aes(x = Food, y = S_InvSlope, fill = StimCond)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5,position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9),alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom="errorbar", alpha=1, position=position_dodge(width=0.9)) +
  guides(fill=guide_legend(title='Stim')) +
  scale_fill_manual(values = c("#FF6347", "#66CDAA")) +
  mytheme +
  labs(title = "Invigoration", x = "Reward type", y = "Invigoration Slope [%/s]")  +
  scale_y_continuous(expand = c(0, 0))


Fig3b <- ave_data_fig3b %>%
  mutate(Food = fct_relevel(Food,"Money", "Food")) %>%
  mutate(StimCond = fct_relevel(StimCond,"Sham", "taVNS")) %>%
  ggplot(aes(x = Food, y = RelFreq, fill = StimCond)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_point(size = 0.5,position = position_jitterdodge(jitter.width = 0.2,
                                             dodge.width = 0.9),alpha= 0.5, color = 'grey') +
  stat_summary(fun.data=mean_cl_normal,colour = "black", width=0.2,size = 0.8,geom = "errorbar", alpha=1, position=position_dodge(width=0.9)) +
  guides(fill=guide_legend(title='Stim')) +
  scale_fill_manual(values = c("#FF6347", "#66CDAA")) +
  mytheme                 +                                 
  labs(title = "Maintenance", x = "Reward type", y = "Relative frequency [%]")+
  scale_y_continuous(expand = c(0, 0))

if (dataset_ana == 'Neuser_orig'){
  Fig3a <- Fig3a + facet_wrap(~StimSide)
  Fig3b <- Fig3b + facet_wrap(~StimSide)
}
# Combine plots in one figure
plt_fig3 <- grid.arrange(Fig3a, Fig3b, nrow=1, ncol=2) 

#ggsave(path = fig_path, filename = "Fig_3ab.pdf", plot=plt_fig3,  width = 8, height =4)
```

**Settings Figure 4** (make long-data format from resfil2 files)

Invigoration

```{r}
if (dataset_ana == 'Neuser_orig'){
  Inv_slope_resfil <- haven::read_sav(paste(home_path, 'Neuser_orig_dat', 'HLM', 'Invigoration', "Inv_slope_resfil2.sav", sep='/'))
} else if (dataset_ana == 'Leiden_repl') {
    Inv_slope_resfil <- haven::read_sav(paste(home_path, '20221004', 'HLM', 'Invigoration', "Inv_slope_resfil2.sav", sep='/'))
}

Inv_slope_resfil = as.data.frame(Inv_slope_resfil)
Inv_slope_resfil <- Inv_slope_resfil %>% 
  rename(ID = L2ID,
         Stimulation = ECSTIMCOND,
         SxDiff = ECI_SDIFF,
         SxRewM = ECI_SREWM,
         SxFood = ECI_SFOOD,
         SxDiffxRewM = ECI_SDRM)

# make long df 
labels = names(Inv_slope_resfil)
# Select variables
var_names = c("ID",
              "Stimulation",
              "SxDiff", 
              "SxRewM", 
              "SxFood", 
              "SxDiffxRewM")

Inv_slope_resfil = Inv_slope_resfil[,match(var_names,labels)]
Inv_slope_resfil = data.frame(Inv_slope_resfil)
Inv_slope_resfil = tidyr::gather(Inv_slope_resfil, value=Val, key=Names, Stimulation:SxDiffxRewM, factor_key=TRUE)
names(Inv_slope_resfil)[names(Inv_slope_resfil) == 'Names'] <- 'Cond'
names(Inv_slope_resfil)[names(Inv_slope_resfil) == 'Val'] <- 'Val'

# for Leiden repl
inv_stimcond_p = 'p = 0.621'
inv_sdiff = '0.058'
```

Maintenance

```{r}
if (dataset_ana == 'Neuser_orig'){
  Relfreq_resfil <- haven::read_sav(paste(home_path,'Neuser_orig_dat', 'HLM', 'Maintenance', "Rel_freq_resfil2.sav", sep='/'))
} else if (dataset_ana == 'Leiden_repl') {
    Relfreq_resfil <- haven::read_sav(paste(home_path, '20221004', 'HLM', 'Maintenance', "Rel_freq_resfil2.sav", sep='/'))
}

Relfreq_resfil = as.data.frame(Relfreq_resfil)
Relfreq_resfil <- Relfreq_resfil %>% 
  rename(ID = L2ID,
         Stimulation = ECSTIMCOND,
         SxDiff = ECI_SDIFF,
         SxRewM = ECI_SREWM,
         SxFood = ECI_SFOOD,
         SxDiffxRewM = ECI_SDRM)

# make long df 
labels = names(Relfreq_resfil)
# Select variables
var_names = c("ID",
              "Stimulation",
              "SxDiff", 
              "SxRewM", 
              "SxFood", 
              "SxDiffxRewM")

Relfreq_resfil = Relfreq_resfil[,match(var_names,labels)]
Relfreq_resfil = data.frame(Relfreq_resfil)
Relfreq_resfil = tidyr::gather(Relfreq_resfil, value=Val, key=Names, Stimulation:SxDiffxRewM, factor_key=TRUE)
names(Relfreq_resfil)[names(Relfreq_resfil) == 'Names'] <- 'Cond'
names(Relfreq_resfil)[names(Relfreq_resfil) == 'Val'] <- 'Val'

# for Leiden repl
#rel_stimcond_p = 'p = 0.500'
```

**Make Figure 4**

```{r}
dens_plt_Inv <- Inv_slope_resfil %>%
  mutate(Cond = fct_relevel(Cond,"SxDiffxRewM", "SxFood", "SxRewM", "SxDiff", "Stimulation")) %>%
  ggplot(aes(x = Val, y = Cond, fill = Cond)) + geom_density_ridges(
  jittered_points = TRUE, position = "raincloud",
  alpha = 0.7, scale = 0.6) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "red", size=0.5) + xlim(-25, 25) + 
  labs(title = "Invigoration", x = "taVNS-induced changes", y = "Density of taVNS-induced changes")


dens_plt_maint <- Relfreq_resfil %>%
  mutate(Cond = fct_relevel(Cond,"SxDiffxRewM", "SxFood", "SxRewM", "SxDiff", "Stimulation")) %>%
  ggplot(aes(x = Val, y = Cond, fill = Cond)) + geom_density_ridges(
    jittered_points = TRUE, position = "raincloud",
    alpha = 0.7, scale = 0.6) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "red", size=0.5) +  xlim(-25, 25) + 
  labs(title = "Maintenance", x = "taVNS-induced changes", y = "Density of taVNS-induced changes") 

if (dataset_ana == 'Leiden_repl') {
  dens_plt_Inv <- dens_plt_Inv + annotate("text", x=10, y=5.5, size = 3, label= inv_stimcond_p)
  dens_plt_maint <- dens_plt_maint + annotate("text", x=10, y=5.5, size = 3, label= rel_stimcond_p)
}

plt_fig4 <- grid.arrange(dens_plt_Inv, dens_plt_maint, nrow=1, ncol=2) 

#ggsave(path = fig_path, filename = "Fig_4.pdf", plot=plt_fig4,  width = 8, height =4)
```

**Settings figure 5a: run robust regression on group level**

```{r}
if (dataset_ana == 'Leiden_repl') {
ave_data_fig5a <- aggregate(cbind(S_InvSlope, Rating_want)
                             ~ ID + StimCond + Food, data = df, FUN = function(x) c(mn = mean(x) ) )
}
if (dataset_ana == 'Neuser_orig') {
ave_data_fig5a <- aggregate(cbind(S_InvSlope, Rating_want)
                             ~ ID + StimCond + Food + StimSide, data = df, FUN = function(x) c(mn = mean(x) ) )
}

# robust regression
rmodel <- robustbase::lmrob(S_InvSlope ~ Rating_want, data = ave_data_fig5a)
```

**Make Figure 5a-b --\> not included in manuscript**

```{r}
if (dataset_ana == 'Neuser_orig') {
  
Fig5a <- ggplot(data = df, aes(x=Rating_want, y=S_InvSlope)) +
  #geom_point() +
  stat_density_2d(aes(fill = stat(level)), geom = "polygon",  bins = 8) +
  geom_smooth(aes(group=StimCond, color = StimCond), method=rlm, se = TRUE) + 
  scale_color_manual(values = c("#FF6347", "#66CDAA")) + 
  mytheme + 
  labs(title = "", x = "Wanting [VAS]", y = "Invigoration Slope [%/s]") +
  facet_wrap(~Food + StimSide , ncol=2, nrow=2) +
  theme(legend.position = "none") +
  scale_fill_viridis(option = "A") + 
  ylim(20, 80) + xlim(0, 100)


} else if (dataset_ana == 'Leiden_repl') {
Fig5a <- ggplot(data = df, aes(x=Rating_want, y=S_InvSlope)) +
  #geom_point() +
  stat_density_2d(aes(fill = stat(level)), geom = "polygon",  bins = 8) +
  geom_smooth(aes(group=StimCond, color = StimCond), method=rlm, se = TRUE) + 
  scale_color_manual(values = c("#FF6347", "#66CDAA")) + 
  mytheme + 
  labs(title = "", x = "Wanting [VAS]", y = "Invigoration Slope [%/s]") +
  facet_wrap(~Food, ncol=2, nrow=1) +
  theme(legend.position = "none") +
  scale_fill_viridis(option = "A")+ 
  ylim(20, 80) + xlim(0, 100)
}
# Fig5b <- ggplot(data = ave_data_fig5b, aes(x=R_Exh, y=S_InvSlope, color=StimCond)) +
#   stat_density_2d(geom = "polygon", alpha=0.2) +
#   geom_smooth(method=lm) + 
#   mytheme + 
#   labs(title = "", x = "Exertion [VAS]", y = "Invigoration Slope [%/s]") +
#   facet_wrap(~Food, ncol=1, nrow=2)

# Fig5b <- ggplot(data = ave_data_fig5b, aes(x=Rating_exh, y=S_InvSlope)) +
#   stat_density_2d(aes(fill = stat(level)), geom = "polygon") +
#   geom_smooth(aes(group=StimCond, color = StimCond), method=lm, se = FALSE) + 
#   scale_color_manual(values = c("#FF6347", "#66CDAA")) + 
#   mytheme + 
#   labs(title = "", x = "Exertion [VAS]", y = "Invigoration Slope [%/s]") +
#   facet_wrap(~Food, ncol=1, nrow=2) +
#   theme(legend.position = "none") +
#   scale_fill_viridis(option = "A") 
Fig5a
#ggsave(path = fig_path, filename = "Fig_5.pdf", plot=Fig5a,  width = 6, height =6)
```

Extra plots looking at the subjective ratings (included in text in methods section)

```{r}

total_subjective <- rbind(df_subjs_vars_neuser , df_subjs_vars_leiden)
total_subjective$Names <- as.factor(total_subjective$Names)
total_subjective$Val <- as.numeric(total_subjective$Val)
plot_A <- total_subjective %>%
    mutate(Names = fct_relevel(Names,"leiden_exertion", "leiden_wanting", "neuser_exertion", "neuser_wanting")) %>%
  ggplot(aes(x = Names, y = Val, fill = Names)) +
  geom_bar(stat='summary', position='dodge', alpha=0.9) +
  geom_jitter(size = 0.5) +
  mytheme +
  guides(fill=guide_legend(title='Subjective ratings')) +
  labs(title = "", x = "", y = "Rating (trial level)")  
```

```{r}
subj_ratings_forest <- total_subjective %>%
    mutate(Names = fct_relevel(Names,"leiden_exertion", "leiden_wanting", "neuser_exertion", "neuser_wanting")) %>%
  ggplot(aes(x = Val, y = Names, fill = Names)) + geom_density_ridges(stat = "binline", bins = 40, scale = 1) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  labs(title = "Invigoration", x = "rating", y = "no. trials")
ggsave(path = fig_path, filename = "subj_ratings_forest.png", plot=subj_ratings_forest,  width = 6, height =6)
```

Some additional sanity checks!

```{r}
# check the ranked data!! 

subj_ratings_forest <- total_subjective %>%
    mutate(Names = fct_relevel(Names,"leiden_exertion", "leiden_wanting", "neuser_exertion", "neuser_wanting")) %>%
  ggplot(aes(x = Val, y = Names, fill = Names)) + geom_density_ridges(stat = "binline", bins = 40, scale = 1) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  labs(title = "Invigoration", x = "rating", y = "no. trials")
ggsave(path = fig_path, filename = "subj_ratings_forest.png", plot=subj_ratings_forest,  width = 6, height =6)
```

```{r}
subj_ratings_forest <- df_subjs_vars_leiden %>%
    mutate(Names = fct_relevel(Names,"leiden_exertion", "leiden_wanting")) %>%
  ggplot(aes(x = Val, y = Names, fill = Names)) + geom_density_ridges(stat = "binline", bins = 40, scale = 1) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  labs(title = "Invigoration", x = "rating", y = "no. trials")
ggsave(path = fig_path, filename = "subj_ratings_forest.png", plot=subj_ratings_forest,  width = 6, height =6)
```

```{r}
# Comparison of VAS between sessions 
df_subjs_vars$SessNr <- as.factor(df_subjs_vars$SessNr)
df_subjs_vars <- df_subjs_vars %>%
  mutate(SessNumber = case_when(SessNr == 1 ~ 'Session1',
                             SessNr == 2 ~ 'Session2'))
subj_ratings_session <- df_subjs_vars  %>%
    mutate(Names = fct_relevel(SessNumber,"Session2", "Session1")) %>%
  ggplot(aes(x = leiden_wanting, y = SessNumber, fill = SessNr)) + geom_density_ridges(stat = "binline", bins = 40, scale = 1) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  labs(title = "Wanting", x = "rating", y = "no. trials")
ggsave(path = fig_path, filename = "subj_ratings_split_Sess_wanting.png", plot=subj_ratings_session,  width = 6, height =6)
```

```{r}
subj_ratings_session_exertion <- df_subjs_vars  %>%
    mutate(Names = fct_relevel(SessNumber,"Session2", "Session1")) %>%
  ggplot(aes(x = leiden_exertion, y = SessNumber, fill = SessNr)) + geom_density_ridges(stat = "binline", bins = 40, scale = 1) + mytheme  + theme(legend.position="None") + theme(axis.line=element_blank())+
  labs(title = "Exertion", x = "rating", y = "no. trials")
ggsave(path = fig_path, filename = "subj_ratings_split_Sess.png", plot=subj_ratings_session_exertion,  width = 6, height =6)
```

```{r}
# make a ploit showing the correlations befween subjective val and invig 

#cor(df$Rating_want, df$S_InvSlope, use="complete.obs")

#a<-plot(df$Rating_want, df$S_InvSlope)
#ggsave(path = fig_path, filename = "cor_inv_wanting.png", plot=a,  width = 6, height =6)

a <- ggplot(df, aes(x=Rating_want, y=S_InvSlope)) + 
  geom_point()+
  geom_smooth(method=lm)
ggsave(path = fig_path, filename = "cor_inv_wanting.png", plot=a,  width = 6, height =6)
a
```

```{r}

b <- ggplot(df, aes(x=Rating_want, y=RelFreq)) + 
  geom_point()+
  geom_smooth(method=lm)
ggsave(path = fig_path, filename = "cor_relfreq_wanting.png", plot=b,  width = 6, height =6)
b
```

```{r}
c <- ggplot(df, aes(x=Rating_exh, y=S_InvSlope)) + 
  geom_point()+
  geom_smooth(method=lm)
c
ggsave(path = fig_path, filename = "cor_inv_exertion.png", plot=c,  width = 6, height =6)
```

```{r}
d <- ggplot(df, aes(x=Rating_exh, y=RelFreq)) + 
  geom_point()+
  geom_smooth(method=lm)
d
ggsave(path = fig_path, filename = "cor_relfreq_exertion.png", plot=d,  width = 6, height =6)
```

Runadditional checks on Bayesian analysis with posterior distribution from original study (variables computed using JASP)

```{r}
# set the median and 95% confidence intervals
median <- 0.291
lower <- 0.072
upper <- 0.511

# set the sample size
n <- 81

# calculate the standard deviation from the confidence interval
sd_est <- (upper - lower) / (2 * qnorm(0.975))

# calculate the standard error of the median
se_median <- sd_est / sqrt(n)

# estimate the normal distribution
mu_est <- median
sigma_est <- sd_est / qnorm(0.75)

# calculate the standard error of the estimated standard deviation
se_sigma <- sd_est / (qnorm(0.75) * sqrt(2 * (n - 1)))

# print the estimated parameters of the normal distribution
cat("Estimated parameters of the normal distribution:\n")
cat("mu = ", mu_est, "\n")
cat("sigma = ", sigma_est, "\n")

# print the standard errors of the estimates
cat("Standard error of the median = ", se_median, "\n")
cat("Standard error of the estimated standard deviation = ", se_sigma, "\n")
```
